---
title: "Homework 6 solutions"
author: "Chufeng Yang"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
```

### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Run `glm` for each of the cities in the dataset.
And extract the adjusted odds ratio (and CI) for solving homicides comparing Black victims to white victims.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI"))  %>% 
  filter(term == "victim_raceWhite")
```

Create a plot that shows the estimated ORs and CIs for each city. 

```{r}
models_results_df %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(limits=c(0,30), breaks=1)
```
We could find the estimated ORs and CIs for each city. And some of them, like Albuquerque,NM or Stockton,CA, have relatively larger OR and wider CI. Moreover, we could find that altought most of our estimated ORs are pretty close to 1,there are more ORs' point estimates are greater than 1, which means that when comparing Black victims to white victims, homicides of white victims are more likely results in arrest. When looking and CIs, some(like a half) are above 1, which means for these cities, we might can conclude that homicides of white victims are more likely results in arrest.


## Problem 2

Find some residuals

```{r}
baby_df = 
  read_csv("./data/birthweight.csv")
```

fit a model

```{r}
model_fit = lm(bwt ~ gaweeks, data = baby_df)
```

```{r}
baby_df %>% 
  modelr::add_residuals(model_fit) %>% 
  ggplot(aes(x = gaweeks, y = resid)) + 
  geom_point()
```

© 2020 GitHub, Inc.
Terms
Privacy
Security
Status
Help
Contact GitHub
Pricing
API
Training
Blog
About
